# analysisToolsLUMA

Functions that can be used to analyse and check LUMA observation data.

## Installation

```{r install, eval=FALSE}

devtools::install_github('kitbenjamin/analysisToolsLUMA') 

library(analysisToolsLUMA)
```
## dependencies


## Plotting time series of instrument variables

Checking time series of data can be useful in diagnosing when, and at what stage of processing, something has gone wrong. *plotData()* will plot raw and processed data.

### Example 1: plotting raw data

Take the simple example of plotting one day of SWT metdata data from /storage/basic/micromet/Tier_raw/RAW/2020/London/SWT/MetData/02

```{r seeMetData}

readLines('man/data/20200227_SWT_MetData.dat', n = 5)

```
To plot this we need to define several variables

```{r defineVars}

instrument <- list(id = 'SWTWXSTATION', site = 'SWT') #define the id and site as it's listed on the metadata site
level <- 'RAW' 
startDate <- as.Date('2020-02-27') #start and end date must be class 'Date'
endDate <- as.Date('2020-02-27')
variables <- c('Tair', 'RH', 'dir', 'WS') # these must also be consistent with the metadata system
tickBreaks <- '2 hours' # where ticks will be on the plot
dateLabelFormat <- '%H:%M' #how the time axis will be formatted
sep <- ',' #the separator in the file
variableColNos = c(2, 10, 8, 5) # what column is each variable represented by
timeColFormat = '%Y-%m-%d %H:%M:%S' # format of the time column
```
Now plot the data

```{r plotwxt, eval=FALSE}

rawWXTPlot <- analysisToolsLUMA::plotLUMAdata(instrument, level, startDate, endDate, variables, tickBreaks, dateLabelFormat, sep = sep, variableColNos = variableColNos, timeColFormat = timeColFormat) 

```


### Example 2: plotting raw data

This time take the slightly more difficult example of this Microlite data from /storage/basic/micromet/Tier_raw/RAW/2020/London/microlite/02

```{r seeData}

readLines('man/data/9178815_2020-02-27.txt', n = 20)

```

Also, save the output to a plots directory

```{r defineMicroVars}

instrument <- list(serial = '9178815') # use the serial number as there's multiple microlites at its site. Equally valid is instrument <- list(id = 'MICROLITE', site = 'BMH', serial = '9178815')
level <- 'RAW' 
startDate <- as.Date('2020-02-20') # plot a few days 
endDate <- as.Date('2020-02-27')
variables <- c('Tair_indoor', 'RH_indoor') 
tickBreaks <- '12 hours' 
dateLabelFormat <- '%j %H:%M' 
sep <- ',' 
variableColNos = c(3, 5) 
timeColFormat = c('%d/%m/%Y', '%H:%M:%S') #time is now over 2 columns so timeColFormat must be a vector
skipRows <- 9 # the first 9 rows are headers
title <- 'My microlite plot' # manually define title this time
SAVEplot <- TRUE
SAVEname <- 'MicroliteTS.png' # dont forget toadd the device (.png)
SAVEpath <- 'man/plots'
SAVEsize <- c(h = 8, w = 5, unit = 'in') # vector for height, width and unit. 
```

```{r plotmicro, eval=FALSE}

rawMicroPlot <- analysisToolsLUMA::plotLUMAdata(instrument, level, startDate, endDate, variables, tickBreaks, dateLabelFormat, sep = sep, variableColNos = variableColNos, timeColFormat = timeColFormat, skipRows = skipRows, title = title, SAVEplot = SAVEplot, SAVEname = SAVEname, SAVEpath = SAVEpath, SAVEsize = SAVEsize) 

```

### Example 3: plotting processed EC data

Plotting processed data is even easier.
Here we plot IMU eddy covariance data:

```{r plotEC, eval=FALSE}

instrument <- list(id = 'LI7500A', site = 'IMU', ECpack = TRUE) #omit EC pack to plot non-ECpack data 
level <- 1 # as an integer
startDate <- as.Date('2020-01-01') 
endDate <- as.Date('2020-02-27')
variables <- c('C_CO2', 'Q_E') 
tickBreaks <- '7 days' # where ticks will be on the plot
dateLabelFormat <- '%d-%m %H' #how the time axis will be formatted
fileTimeRes = '30min' # for processed data the file time resolution must be manually defined as there's often several options.
lOneLicorPlot <- analysisToolsLUMA::plotLUMAdata(instrument, level, startDate, endDate, variables, tickBreaks, dateLabelFormat, fileTimeRes) 
```

plotLUMAdata() constists of 2 main functions that
1. get the data
2. plots the data

These can each be done seperately using these two functions:
```{r sepFunctions, eval=FALSE}
allData <- getLUMAdata

finalPlot <- plotTimeSeries
```

Use ?getLUMAdata() and ?plotTimeSeries for more details.

Notes
* doesn't deal with changes in site and time res
* instrument can just be a serial number, or can be site, id and serial. I is faster to define site and ID.
* for level RAW fileTimeRes can either be defined manually or it will be obtained from the metadata system
