# analysisToolsLUMA

Functions that can be used to analyse and check LUMA observation data.

## Installation

```{r install, eval=FALSE}

devtools::install_github('kitbenjamin/analysisToolsLUMA') 

```
## dependencies


## Plotting time series of instrument variables

Checking time series of data can be useful in diagnosing when, and at what stage of processing, something has gone wrong. *plotData()* will plot raw and processed data.

### Example 1: plotting raw data

Take the simple example of plotting one day of SWT metdata data from /storage/basic/micromet/Tier_raw/RAW/2020/London/SWT/MetData/02

```{r seeMetData}

readLines('data/20200227_SWT_MetData.dat', n = 5)

```
To plot this we need to define several variables

```{r defineVars}

instrument <- list(id = 'SWTWXSTATION', site = 'SWT') #define the id and site as it's listed on the metadata site
level <- 'RAW' 
startDate <- as.Date('2020-02-27') #start and end date must be class 'Date'
endDate <- as.Date('2020-02-27')
```


Take the example of this Microlite data from /storage/basic/micromet/Tier_raw/RAW/2020/London/microlite/02

```{r seeData}

readLines('data/9178815_2020-02-27.txt', n = 20)

```

To plot this day of data we need to define several variables

